\thesistitle

### 2019-08-20 sections/discussion.tex
Conclusion
2R and 3R thresholds discussion

In this chapter, we discuss the results of our research and experiments.
% TODO: Sander - ik mis ergens in chapter nog interpretatie van je resultaten van H6, of heb ik iets gemist?

@@

\subsection{Clone Types}
In this section, we discuss the differences between clone types 1-3 and 1R-3R. In Figure \ref{fig:typeres} we see that the difference between T1R and T1 is relatively small (11\% more cloned nodes found for T1). Often textually equal code is also functionally equal. The difference between T2R and T2 is bigger (34.7\% more cloned nodes for T2). The main reason for this is that T2R does not allow any variability in types, wheareas T2 allows any variability in types. T3R and T3 only a little bit higher than T2R and T2.

Regarding performance (Figure~\ref{fig:performance}, there is a notable difference between the refactoring-oriented clone types and the literature clone types. Type 1R-3R take about 6 times longer to detect than type 1-3. The main reason for this is type resolution: finding the fully qualified identifiers of type-, variable- and method-references.

>>>>

In this chapter, we discuss the results of our research and experiments.

@@

\subsection{Clone Types}
In this section, we discuss the differences between clone types 1-3 and 1R-3R.

\subsubsection{Found nodes}
In Figure \ref{fig:typeres} we see that the difference between T1R and T1 is relatively small (11\% more cloned nodes found for T1). Often textually equal code is also functionally equal. The difference between T2R and T2 is bigger (34.7\% more cloned nodes for T2). The main reason for this is that T2R does not allow any variability in types, wheareas T2 allows any variability in types. T3R and T3 only a little bit higher than T2R and T2.

\subsubsection{Performance}
Regarding performance (Figure~\ref{fig:performance}, there is a notable difference between the refactoring-oriented clone types and the literature clone types. Type 1R-3R take about 6 times longer to detect than type 1-3. The main reason for this is type resolution: finding the fully qualified identifiers of type-, variable- and method-references.

\subsubsection{Type 2R Variability}
In Figure~\ref{fig:t2rgraph} we show the increase of cloned nodes for a higher variability between clone instances. This graph is logaritmic: as the variability increases, the increase in nodes decreases. This implies that semantical equality increases the chances that tokens are equal.

\subsubsection{Type 3R Gap Size}
In Figure~\ref{fig:t3rgraph} we show the decrease in clone classes and the increase in cloned nodes when we increase the type 3R gap size threshold. We measure this threshold from a gap size of 0-200\%. In the graph, we see that both lines are rather linearly with minor jumps at certain thresholds. The jumps are at 33\%, 50\%, 100\%, 150\% and 200\%. The jump at 50\% is the largest. This makes sense regarding the nature of the threshold. At 50\%, all clone instances of 2 nodes with a gap of one node will merge into type 3R clones.

The line denoting the number of clone classes seems a bit exponential whereas the line denoting cloned nodes is mostly linear. This also makes sense regarding the nature of the threshold. As we get into higher gap size percentages, fewer clones merge (thus the decrease in amount of clone classes merging). However, at these higher gap size percentages the gaps contains more nodes (thus the amount of cloned nodes being linear).

### 2019-08-20 sections/results.tex
PRI
Threats to validity
2R and 3R thresholds discussion

\subsection{Type 2R Variability Threshold}
To determine the influence of the type 2R variability threshold on the amount of found nodes, we ran CloneRefactor for all variability percentages (0\% meaning no variance in expressions, 100\% meaning any variance in expression). Figure \ref{fig:t2rgraph} shows the results.

@@

\subsection{Relation}
Table~\ref{tab:relation_refactor} shows our data regarding how different relations influence maintainability. We have marked rows based on less than 100 refactorings red, as their result does not have statistical significance.

@@

\begin{figure}[H]
  \includegraphics[width=0.8\columnwidth]{img/arguments}
  \caption{Influence of number of method parameters on system maintainability.}
  \label{fig:arguments}
\end{figure}

>>>>

\subsection{Type 2R Variability Threshold}
To determine the influence of the type 2R variability threshold on the amount of found nodes, we ran CloneRefactor for all variability percentages (0\% meaning no variance in expressions, 100\% meaning any variance in expressions). Figure \ref{fig:t2rgraph} shows the results.

@@

\subsection{Relation}
Table~\ref{tab:relation_refactor} shows our data regarding how different relations influence maintainability. We mark rows based on less than 100 refactorings red, as their result does not have statistical significance.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\columnwidth]{img/arguments}
  \caption{Influence of number of method parameters on system maintainability.}
  \label{fig:arguments}
\end{figure}
